A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-07-08 papers/earths-future/submission.tex
Update funding

This work was supported by \acrfull{noaa} through the Mid-Atlantic Regional Integrated Sciences and Assessments (MARISA) program under \gls{noaa} grant NA16OAR4310179 and by the Penn State Center for Climate Risk Management.
JDG thanks Rice University for support.
KK thanks Dartmouth College for support.
The authors thank
Tor Erlend Fjelde,
Vivek Srikrishnan,
Adam Pollack,
and Sitara Baboolal
for helpful comments.

>>>>

This work was supported by \acrfull{noaa} through the Mid-Atlantic Regional Integrated Sciences and Assessments (MARISA) program under \gls{noaa} grant NA16OAR4310179 and through the Penn State Initiative for Resilient Communities (PSIRC) by a Strategic Plan seed grant from the Penn State Office of the Provost, with co-support from the Center for Climate Risk Management (CLIMA), the Rock Ethics Institute, Penn State Law, and the Hamer Center for Community Design.
JDG thanks Rice University for support.
KK thanks Dartmouth College for support.
The authors thank
Tor Erlend Fjelde,
Vivek Srikrishnan,
Adam Pollack,
and Sitara Baboolal
for helpful comments.
